Supplemental Materials, Methods and Results

### 2022-04-13 supp/Supplemental Materials and Methods.Rmd
replaced climae_data with data_wide as data_long seems to be missing quite a lot of data. Need to re-check the re-organisation of the data

    # Get the unique species lat and long data which will be used to extract climate data for each ppulation / species for wild derived sources.
    climate_data <-  data_long %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  group_by(species_full)%>%
                  mutate(n = length(habitat)) %>%
                  dplyr::select(species_full,  habitat, source, n, lat, long) %>% 
                  distinct(species_full, habitat, n, source, lat, long) 
      write.csv(climate_data, file = "../data/climate_data/Species_LatLong_plusHabitat.csv", row.names=FALSE)

>>>>

    # Get the unique species lat and long data which will be used to extract climate data for each ppulation / species for wild derived sources.
    climate_data <-  data_wide %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  dplyr::select(species_full,  habitat, source, lat, long) %>% 
                  distinct(species_full, habitat, source, lat, long) 
      write.csv(climate_data, file = "../data/climate_data/Species_LatLong_plusHabitat.csv", row.names=FALSE)
